Julianna's algal metrics wrangling code

### 2024-07-30 julianna_algalMetric_wrangling.Rmd
Created the model markdown

```{r save}
# write_csv(quadData, here("algal_metrics_quadrat.csv"))
```

@@

```{r save dataframe}
# write_csv(siteData, here("algal_metrics_site.csv"))
```

@@

```{r save}
# write_csv(alltimeCV, here(here("algal_metrics_all_time.csv")))
```

>>>>

```{r save}
# write_csv(quadData, here("data/algal_metrics_quadrat.csv"))
```

@@

```{r save dataframe}
# write_csv(siteData, here("data/algal_metrics_site.csv"))
```

@@

```{r save}
# write_csv(alltimeCV, here(here("data/algal_metrics_all_time.csv")))
```
